\documentclass[letterpaper,10pt]{article}

\usepackage{makecell}
\usepackage[link=off]{phonenumbers}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\usepackage[margin=0.3in]{geometry}
% Adjust margins
\addtolength{\oddsidemargin}{-0.0in}
\addtolength{\evensidemargin}{-0.0in}
\addtolength{\textwidth}{0in}
\addtolength{\topmargin}{5pt}
\addtolength{\textheight}{0.0in}

\urlstyle{same}

\hypersetup{
    colorlinks=true,
    linkcolor=blue!50!red,
    linkbordercolor=red,
    urlcolor=blue!70!black
}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\def \ifempty#1{\def\temp{#1} \ifx\temp\empty }

\newcommand{\resumeItem}[2]{
    \item\small{
        \ifempty{#1}#2\else\textbf{#1}{: #2 \vspace{-2pt}}\fi
    }
}

\usepackage[dvipsnames]{xcolor}
\definecolor{mygray}{gray}{0}
\usepackage{fancybox}

\usepackage{lmodern}
\usepackage{tikz}

% Style definition
\tikzset{rndblock/.style={rounded corners,rectangle,draw,outer sep=0pt}}

% Command Definition
% 1 optional to customize the aspect, 2 mandatory: text to be framed
\newcommand{\tframed}[2][]{\tikz[baseline=(h.base)]\node[rndblock,#1] (h) {\color{black}{#2}};}

\newcommand*{\mystrut}{\rule[-0.2\baselineskip]{0pt}{0.8\baselineskip}}
\newcommand{\skill}[1]{\tframed[lightgray]{\mystrut#1}}


\newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1}       & \textcolor{mygray}{#2}                 \\
        \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeExpSubheading}[5]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1}       & \textcolor{mygray}{#2}                 \\
        \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
        {\scriptsize#5}
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeProjSubheading}[4]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1}      & \textcolor{mygray}{#2}                 \\
        \scriptsize {#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\usepackage{changepage}
\newcommand{\resumeDesc}[1]{\begin{adjustwidth}{5pt}{0pt}\vspace{-2pt}{\small{#1}}\end{adjustwidth}}


\begin{document}

\vfill\noindent
\begin{tabular}[t]{@{
\vspace{0.5ex}
}left}
\textbf{\large{Vladislav Pakhomov}} \\
\address{
+7\hspace{0.5ex}909\hspace{0.5ex}216\hspace{0.5ex}36\hspace{0.5ex}40 $\cdot$ Moscow, Russia
}
\end{tabular}
\hfill % move it to the right
\begin{tabular}[t]{@{
\vspace{0.5ex}
}center}
\href{mailto:vladislavpakhomov03@gmail.com}{\color{black} vladislavpakhomov03@gmail.com} \\

\href{https://github.com/vlpakhomov}{\color{black} \faGithub}

\href{https://t.me/vlpakhomov}{\color{black} \faTelegram}
\end{tabular}


\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{National Research Nuclear University MEPhI}
{Moscow, Russia}
{Information Security}
{Sept. 2021 - Aug. 2025 (Present)}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart

\resumeExpSubheading
{\href{https://crtex.ru/en}{Crtex}}{Moscow, Russia}
{Jun+ Go Developer}{December 2023 - Present}
{\skill{Go} \skill{gRPC} \skill{Clean Architecture} \skill{Temporal} \skill{Apache Kafka} \skill{System Design} \skill{Microservice Architecture} \skill{Tracing} \skill{Monitoring} \skill{k8s} } 
\resumeDesc{
\begin{itemize}
\item Designed a microservice architecture by Dark energy forces and Dark matter forces.
\item Implemented asynchronous requests using Apache Kafka.
\item Tracing of requests by otel.
\item Monitoring of requests by prometheus and visualization by grafana.
\item Used Temporal for distributed operations and eventually consistency.
\end{itemize}}

\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart

\resumeProjSubheading
{\href{https://github.com/vlpakhomov/redditclone}{redditclone}}{}
{\skill{Go} \skill{RESTful API} \skill{Clean Architecture} \skill{MySQL} \skill{MongoDB} \skill{Reddis} \skill{GoMock} \skill{JWT} \skill{Docker}}{November 2023}
\resumeDesc{
\begin{itemize}
\item Designing API according to REST principles
\item Have authorization using JWT token and Middleware pattern
\item Thread-Safety application
\item Almost 100\% coverage in Unit Testing
\item Designing each component according to SOLID principles
\item Platform independent application deployment with Docker
\end{itemize}
}

\resumeProjSubheading
{\href{https://github.com/vlpakhomov/url-shortener}{url-shortener}}{}
{\skill{Go} \skill{RESTful API} \skill{gRPC} \skill{MVC} \skill{PostgreSQL} \skill{Zap logger} \skill{Docker}}{June 2023}
\resumeDesc{
\begin{itemize}
\item Designing API according to REST principles
\item Thread-Safety application
\item Flexible application configuration using config parser
\item Multi-Level Logging usin Zap package
\item Platform independent application deployment with Docker
\end{itemize}
}


\resumeSubHeadingListEnd

\section{Achievements}
\resumeSubHeadingListStart

\resumeProjSubheading
{{\href{https://education.vk.company/}{Development of web services on Golang by VK Education}}}{}
{\skill{Go} \skill{Backend/Web development} \skill{Concurrency} \skill{Unit testing}  \skill{Clean Architecture} \skill{OOP} \skill{SQL/NoSQL databases in Go}}
{Sept. 2023 - Dec. 2023}
\resumeDesc{
\begin{itemize}
\item Wrote clean, secure and scalable code during all course
\item Got basic skills in web, testing, work with databases from go.
\item Done six big homework related directly to the business
\item Took part in the final hackathon in VK
\item Got on the leaderboard in the final of the course
\end{itemize}
}


\resumeProjSubheading
{{\href{https://github.com/vlpakhomov/mipt-cpp}{C++ by MIPT}}}{}
{\skill{C++11} \skill{Low-level development} \skill{Algorithms} \skill{Data Structures} \skill{OOP} \skill{SOLID} \skill{CMake} \skill{Valgrind/ASAN} }
{Jan. 2023 - May 2023}
\resumeDesc{
\begin{itemize}
\item Wrote clean, secure and scalable code during all course
\item Got basic skills in low-level programming on C++11.
\item Got a powerful theoretical base in designing programs, algorithms and data structures
\item Directly work with low-level testing utilities
\end{itemize}
}

\resumeSubHeadingListEnd

\section{Programming Skills}
\resumeSubHeadingListStart
\item{
\textbf{Languages}{: Go, C++11 }
}\vspace{-7pt}
\item{
\textbf{Technologies}{: TCP/IP, gRPC, SQL, Git, K8s, Docker, Bash, Apache Kafka, Temporal, PostgreSQL, MySQL, MongoDB, Redis, Clean Architecture, MVC, SOLID, GoF, RESTful/RPC API}
}
\vspace{-7pt}
\item{
\textbf{Knowledge}{: Algorithms, Data Structures, Networks, Operating Systems, Databases, Concurrency, Tracing, Monitoring, Architectural patterns, OOP, System Design Patterns}
}
\resumeSubHeadingListEnd

\end{document}
